\fancypagestyle{abstractStyle}{
	\fancyhf{}
	\fancyhead[C]{\zihao{5} \songti 摘\hspace{1em}要}
}
\thispagestyle{abstractStyle} 

\section*{\zihao{3} \centering 计算机学院答辩管理系统的设计与实现}
%\addcontentsline{toc}{section}{摘要}  % 摘要是否包括进目录中

\begin{center}
	\textbf{\zihao{-3} 摘\hspace{1em}要}
\end{center}
\vspace{2em}

随着互联网的高速发展，人们生活在数字化的信息时代。相比以前较难获取信息，当下的人们可以十分便捷地接触到海量数据，以至于人们淹没在数据中难以快速的制定合适的决策。在校园中，学院的日常教务工作同样面临着这个难题，迫切地需要将已有的业务逻辑线上化。

随着学生毕业人数逐年增加，传统的大学生教务管理方案面临着挑战。这些方法往往存在性能问题，落后的系统也不能满足快速响应、较大吞吐量和现代应用服务安全的要求。因此，本文设计了一个基于Meteor框架的高性能云信息系统，实现了高校毕业设计答辩管理。实验结果表明，与 PHP、ASP 等技术实现的传统信息系统相比，该系统具有更快的响应速度和吞吐量。为传统的高校毕业管理制度提供了可靠的解决方案。

根据开发高校毕业设计答辩管理系统的需求，我们首先将功能抽象化，确定了毕业设计答辩工作的流程，以及用户角色划分。采用了JS全栈开发，选用了 Meteor 开发框架，数据库采用MongoDB，以及将React作为前端数据渲染引擎。这些都是目前web开发中最为流行的工具。

我们遵循了Meteor和React所提倡的理念：前后端之间只对数据进行交互，对数据的渲染由客户端完成而非服务器端。包括对数据库读写的相关逻辑，都在客户端中被实现，节省了发送和接受请求的过程，同时安全性也是有保证的。在实际的开发中，我们感受到了这些特性所带来的便利性，那就是应用逻辑清晰，并且开发速度很快。也正是由于将数据的渲染交给了浏览器，从而大大降低了服务器的负载，在最后的压力测试中表现出了很好的成绩。

\vspace{1em}
\noindent
\textbf{关键词：}信息系统；教学辅助管理系统；Web开发；JavaScript；Node.js


\clearpage
\fancypagestyle{abstractStyleEn}{
	\fancyhf{}
	\fancyhead[C]{\zihao{5} ABSTRACT}
}
\thispagestyle{abstractStyleEn} 

\section*{\songti\zihao{3} \centering \textbf{Design and Implementation of the Computer College Graduation Inspection Management System}}
%\addcontentsline{toc}{section}{Abstract}  % 英文摘要是否包括进入目录

\begin{center}
	\textbf{\zihao{-3}ABSTRACT}
\end{center}
\vspace{2em}

With the rapid development of the Internet, people are living in the digital information age. Compared with the previous difficult to obtain information, people in the moment can easily access to massive data, so that it is difficult for people to drown out the data quickly to make appropriate decisions. On the campus, the daily academic work of the college is also facing this problem, and it is urgent to online the existing business logic.

With the increase in the number of students graduating year by year, the traditional management plan for college student education is facing challenges. These methods often have performance problems, and backward systems cannot meet the requirements for fast response, large throughput, and modern application service security. Therefore, this paper designs a high-performance cloud information system based on Meteor framework, which realizes the management of college graduation design defense. Experimental results show that the system has faster response speed and throughput than traditional information systems implemented by PHP, ASP and other technologies. It provides a reliable solution for the traditional university graduation management system.

According to the requirements for the development of graduation design defense management system in colleges and universities, we first abstracted the function, determined the process of graduation design reply work, and the division of user roles. JS full stack development was used, the Meteor development framework was chosen, the database was MongoDB, and React was used as the front-end data rendering engine. These are the most popular tools in web development.

We followed the philosophy advocated by Meteor and React: only the data is exchanged between the front and back ends, and the rendering of the data is done by the client instead of the server. Including the relevant logic for reading and writing to the database is implemented in the client, saving the process of sending and receiving requests, and the security is also guaranteed. In the actual development, we have felt the convenience brought by these features, that is, the application logic is clear and the development speed is very fast. It is also due to the rendering of the data to the browser, which greatly reduces the load on the server and shows good results in the final stress test.

\vspace{1em}
\noindent 
\textbf{Keywords: }Information System; Teaching Aid Management System; Web Development;\\JavaScript; Node.js;

